---
title: "BLAST"
output: html_notebook
---


# Introduction
This notebok show an example usage of docker to perform a blast between two plasmid sequence. 



# Plasmid Sequence download

We start by downloading the plastmid sequences from NCBI
```{r}
download.file("https://www.ncbi.nlm.nih.gov/sviewer/viewer.cgi?tool=portal&save=file&log$=seqview&db=nuccore&report=fasta&id=2163280802&conwithfeat=on&withparts=on&hide-cdd=on&ncbi_phid=null","CP083077.fasta")
download.file("https://www.ncbi.nlm.nih.gov/sviewer/viewer.cgi?tool=portal&save=file&log$=seqview&db=nuccore&report=fasta&id=359422634&conwithfeat=on&withparts=on&hide-cdd=on&ncbi_phid=null","JN626286.fasta")
```


We call blast through docker, to get help on the available parameters
```{bash}
docker run --rm ncbi/blast blastn -help
```


Now we call BLAST to align the two plasmid sequences and generate the alignment regions
```{bash}
docker run --rm -v $(pwd):/data ncbi/blast blastn -query /data/CP083077.fasta -subject /data/JN626286.fasta -outfmt 6 -out /data/blast_output.tab
```



# Load alignment output in R
```{r}
aln <- read.table(
  "blast_output.tab",sep="\t",
  col.names = c('qaccver','saccver','pident','length','mismatch','gapopen','qstart','qend','sstart','send','evalue','bitscore')
)
```


# Display alignment results
```{r}
library(ggplot2)
ggplot(aln) + 
  geom_segment(aes(x=qstart,xend=qend,y=sstart,yend=send),linewidth=1) + 
  coord_equal() + xlab("query") + ylab("subject")
```





